%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Matvey} \headerlastnamestyle{Panteleev} \\
	\vspace{2mm}
	{\faEnvelope\ m.d.panteleev@gmail.com} | {\faMapMarker\ St. Petersburg, Russian Federation}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{BS in Robotics \& Mechatronics}
	{St.Petersburg Polytechnic University (SPbPU)}
	{St. Peterburg}
	{Sep 2018 – June 2022}
	{GPA: 4.9/5.0}
\end{cventries}

\vspace{-2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Robotics Engineer}
	{Russian State Scientific Center for Robotics and Technical Cybernetics}
	{St.Petersburg}
	{November 2021 – Present}
	{\begin{cvitems}
		\item {Developed tools for automatic radio channel bandwidth testing.}
		\item {Participated in robotic systems development in various roles}
		\end{cvitems}}
	\cventry
	{Internship}
	{Innopolis University}
	{}
	{August 2021 – August 2021}
	{}
\end{cventries}
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Tools:  & {\skill{ C/C++, Python, ROS, OpenCV, Matlab, Embedded Development}} \\
		CAD:  & {\skill{ Fusion 360, Altium Designer, Solidworks, Visual Components}} \\
		English:  & {\skill{ C1 (IELTS 8.0)}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-7mm}
\cvsection{Projects}
\begin{cventries}
	\cventry
	{A stereo system based on orthogonally placed fisheye cameras. Allows to get depth data for a wide range of camera configurations.}
	{Orthogonal Fisheye Stereo Vision System}
	{OpenCV, C++, Unity}
	{https://github.com/QuOzer/fisheye\_stereo}
	{}
	
	\vspace{-5mm}
	\cventry
	{A ROS-controlled 5DoF manipulator based on STM32 MCU}
	{Manipulator}
	{C, STM32, ROS}
	{https://github.com/QuoZer/Tertiarm\_ROS-STM}
	{}
	
	\vspace{-5mm}
	\cventry
	{A Visual Components based application for cobot programming in VR. The project is being developed into a startup with a state grant help.}
	{VR Cobot Trainer}
	{Python, Visual Components}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{A ROS wrapper for Unitree A1 quadruped robot API. Tested with SLAM application.}
	{Quadruped Robot ROS integration}
	{C++, ROS}
	{https://github.com/SailorTheMan/unitree\_slam}
	{}
	
	\vspace{-5mm}
\end{cventries}
\cvsection{Awards}
\begin{cvhonors}
	\cvhonor
	{NTI Contest winner team}
	{Assembled and lead a team that won an Intellectual Robotic Systems track of National Technical Initiative Contest.}
	{Innopolis university}
	{May 2021}
\end{cvhonors}
\ 
\end{document}